A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-05-17 04_Severity_MetaAnalysis.Rmd
try meta-analysis of the log response ratio

# scale to 100% 
PM_dat_D$L_yi_p  <- log(PM_dat_D$yi_percent + 1 )
PM_dat_D$L_vi_p  <- log(PM_dat_D$vi_percent +1 )
```

@@

Finally lets assess the percent severity
```{r Metafor-Sev-analysis, cache=TRUE}
PMsev_mvPer <- rma.mv(
   yi = L_yi_p,
   V = L_vi_p,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = PM_dat_D
)

>>>>

# scale to 100% 
# create column giving the respective disease severity in the control 
PM_dat_D$yi_Cp <- unlist(apply(PM_dat_D, 1, function(x1){

   mean(PM_dat_D[PM_dat_D$trial == x1[["trial"]] &
               PM_dat_D$spray_management == "control", "yi_percent"])
}))

# calculate response ratio
PM_dat_D$L_yi_p  <- log((PM_dat_D$yi_percent / PM_dat_D$yi_Cp) + 1)

# transform variance as per Paul et. al 2007
PM_dat_D <- 
   PM_dat_D %>%
   mutate(L_RR_v = vi *(1/replicates * (yi_percent ^ 2) + 1/replicates * (yi_Cp^2)))
```

@@

Finally lets assess the percent severity
```{r Metafor-Sev-analysis, cache=TRUE}
# remove controls for response ratio meta-analysis
dat_RR <- PM_dat_D[PM_dat_D$spray_management != "control",]

PMsev_mvPer <- rma.mv(
   yi = L_yi_p,
   V = L_RR_v,
   mods = ~ spray_management,
   method = "ML",
   random = list( ~ spray_management | trial, ~ 1 | id),
   struct = "UN",
   control = list(optimizer = "optim"),
   data = dat_RR
)
